### 2021-11-09 NSF2021/Description/specificaim2.tex
worked on SA2

\subsubsection{Iterative methods for the Allen-Cahn HAP model}
\label{subsec:AC}
In the PIs collaboration, they have developed numerical methods to
solve~\eqref{eq:SL} when $f(u) = u^2$. With this choice of $f(u)$, the
resulting PDE is the linear screened Laplace equation which is
efficiently solved with a double-layer potential representation. For a
more general $f$, such as a double well potential, we will interpret the
solution of~\eqref{eq:SL} as a root finding problem for the operator
\begin{align*}
  F[u] = -\rho \Delta u + f'(u).
\end{align*}

>>>>

\subsubsection{Iterative methods for the Allen-Cahn HAP model}
\label{subsec:AC}
In the PIs collaboration, they have developed numerical methods to
solve~\eqref{eq:SL} when $f(u) = u^2$. With this choice of $f(u)$, the
resulting PDE is the linear screened Laplace equation which is
efficiently solved with a double-layer potential representation. For a
more general $f$, such as a double well potential, we will interpret the
solution of~\eqref{eq:SL} as a root finding problem for the operator
\begin{align*}
  F[u] = -\rho^2 \Delta u + f'(u).
\end{align*}
This non-linear PDE will be solved with Newton's method
\begin{align*}
  u^{N+1} = u^{N} - dF^{-1} F(u^N),
\end{align*}
where $dF = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative of
$F$. As expected, the biggest challenge amounts to solving
\begin{align}
  \label{eq:NewtonUpdate}
  - \rho^2 \Delta v + f''(u^{N}) v = F[u^N].
\end{align}
For a general double well potential $f(u)$, this is a variable
coefficient elliptic PDE, and developing an integral equation
formulation is challenging. We propose to instead use an inexact
Newton's method where $dF^{-1}$ is defined in terms of the piecewise
quadratic approximation
\begin{align*}
  f(u) \approx bu + \begin{cases}
    a(u - U_1)^2, &\mbox{if } u \leq (U_0 + U_1)/2 \\
    (u - U_2)^2, &\mbox{if } u > (U_0 + U_1)/2.
  \end{cases}
\end{align*}
In this case, the update step of Newton's method~\eqref{eq:NewtonUpdate}
amounts to solving the piecewise constant PDE
\begin{align}
  \label{eq:screenedPoisson}
  -\rho^2 \Delta v + 
  \left(
  \begin{cases}
    2a, &\mbox{if } u^{N} \leq (U_0 + U_1)/2 \\
    2, &\mbox{if } u^{N} > (U_0 + U_1)/2
  \end{cases}
  \right)
  v = F[u^N],
\end{align}
which is a screened Poisson equation with piecewise a constant screening
coefficient. Solutions of the screened Poisson equation can be written
in terms of volume and layer potentials. We first define the level set
$\Gamma = \{\xx \:|\: \uu(\xx) = (U_0 + U_1)/2 \}$ which separates the
domain $\Omega$ into two regions. Then, assuming that the particles are
all contained in the hydrophobic region, a solution of the screened
Laplace equation (i.e.~equation~\eqref{eq:screenedPoisson} when $F[u^N]
= 0$) is
\begin{align*}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nn_\yy} K_0 \left(
    \frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) ds_\yy + 
    \frac{1}{2\pi} \int_{\Gamma} K_0 \left(
    \frac{|\xx - \yy|}{\rho} \right) \eta(\yy) ds_\yy,
\end{align*}
